climatrends: Precipitation and temperature indices for climate variability analysis in R

### 2020-05-18 inst/paper/paper.Rmd
update-gdd-function

Where $T_{max}$ is the maximum temperature in the given day, $T_{min}$ is the minimum temperature in the given day and $T_{0}$ is the minimum temperature for growth (as per the physiology of the focal organism).

@@

Additionally, the function may return the number of days that a given organism required to reach a certain number of accumulated degree-days or the raw gdd in each observed day. These values are defined by 'ndays' or 'gdd' and can be adjusted using the argument `return.as`. The required accumulated gdd is defined with argument `degree.days`. For example, the Korean pine (*Pinus koraiensis*) requires 105 $^\circ C$ accumulated gdd to onset of photosynthesis [@JWu2013]. In that case, the function will calculate the growing degree-days ($gdd$) and sum up the values until it reaches the defined gdd (105 $^\circ C$) and return the number of days needed in the given season ($GDD_{ndays}$), as follows.

@@

$$\parallel GDD_{ndays} \parallel \: = \; \sum^{ggd_1}_{gdd_n}$$

>>>>

Where $T_{max}$ is the maximum temperature in the given day, $T_{min}$ is the minimum temperature in the given day and $T_{0}$ is the minimum temperature for growth (as per the physiology of the focal organism or ecosystem averages).

@@

By default, the function returns the degree-days that is accumulated over the time series. Additionally, the function may return the daily values of degree-days or the number of days that a given organism required to reach a certain number of accumulated degree-days. These values are defined by 'acc', 'daily' or 'ndays' and can be adjusted using the argument `return.as`. The required accumulated gdd is defined with argument `degree.days`. For example, the Korean pine (*Pinus koraiensis*) requires 105 $^\circ C$ accumulated gdd to onset of photosynthesis [@JWu2013]. In that case, the function will calculate the growing degree-days ($gdd$) and sum up the values until it reaches the defined gdd (105 $^\circ C$) and return the number of days needed in the given season ($GDD_{ndays}$), as follows.

@@

$$\parallel GDD_{ndays} \parallel \: = \; ggd_1 \;+ \; ...  \; +  \; gdd_n$$
